### 2013-09-16 manuscripts/reply/reply.tex
Work on reply intro.

\newpage
\noindent \ldots

>>>>

\newpage
\noindent Both papers are largely in agreement.
In fact, \citet{Hickerson2013} reiterate a lot of the discussion of
\citet{Oaks2012} regarding the impact of broad uniform priors on Bayesian model
choice.
The main differences in their perspectives are centered around
(1) the means by which broad uniform priors cause the poor behavior of \msb,
and
(2) how to potentially ameliorate this issue.

\citet{Oaks2012} conclude the primary mechanism by which broad priors cause the
poor behavior of the method is likely the low marginal likelihoods of
parameter-rich models integrated over vast parameter space with low probability
of producing the data, yet relatively high prior density \citep[this is often
referred to as Lindley's paradox;][]{Lindley1957}.
Note, this suggests the bias is extrinsic to \msb, and the numerical
approximation machinery of the method could be sound.
\citet{Hickerson2013} take a more pessimistic view of the bias, and suggest the
bias is intrinsic to \msb, i.e., the method's rejection algorithm is
inefficient and will be increasingly biased as the overall space of the model
increases, either as a function of the number of taxon pairs or the width of
the uniform priors on nuisance parameters.
